---
title: "week14"
author: "Mathi Manavalan"
date: "4/24/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries
```{r message=FALSE, warning=FALSE}
library(RMariaDB)
library(tidyverse)
```


## Data Import and Cleaning

In this first section, I am creating a connection to the database and exploring what is available to me (commented out, as it is not necessary past exploration).
```{r include=FALSE}
con <- dbConnect(MariaDB(),
                 user = "rnlander_8960r",
                 password = "rTCo.4vQ2vc-",
                 host = "tntlab.org")

#dbExecute(con, "SHOW DATABASES")

dbExecute(con, "USE rnlander_8960")

# dbGetQuery(con, "SHOW TABLES")
# 
# dbGetQuery(con, "SELECT * FROM demos")
# 
# dbGetQuery(con, "SELECT * FROM responses")
# 
# dbGetQuery(con, "SELECT * FROM socialmedia")

```

Here, I am using SQL to collect the data required to answer the question *Do people that use more social media platforms (i.e., a larger count of platforms) have greater acceptance of privacy intrusions (i.e., a higher mean score across the 4-point scale), and do these differences vary by age?* .

To do this, I first inner-joined the *responses* table with the *socialmedia* table using *responses.smu_code* and *socialmedia.code* to collect all the privacy questions' responses as well as social media usage information. Then, I inner-joined this with the *demos* table to be able to collect the ages of participants. 

Finally, I saved the resulting table as a data frame in *sql_tbl*.

```{r}

sql_tbl <- dbGetQuery(con, "SELECT ident, age, facebook, twitter, instagram, youtube, snapchat, other, rec_events, rec_products, rec_friends, rec_policial

           FROM responses AS r
           INNER JOIN socialmedia AS s
           ON r.smu_code = s.code
           
           INNER JOIN demos AS d
           ON r.ident = d.participant_num
           
           ORDER BY ident
           ")


# gets table containing which social media are used; WITH ident of participant
#smTable <-
# dbGetQuery(con, "SELECT ident, facebook, twitter, instagram, youtube, snapchat, other
#            FROM responses AS r
#            INNER JOIN socialmedia AS s
#            ON r.smu_code = s.code")


# gets table containing all 4 privacy questions' responses and includes age; WITH participant_num
#privTable <-
# dbGetQuery(con, "SELECT participant_num, age, rec_events, rec_products, rec_friends, rec_policial, facebook, twitter, instagram, youtube, snapchat, other
# 
#            FROM demos AS d
#            INNER JOIN responses AS r
#            ON d.participant_num = r.ident
# 
#            WHERE rec_events <> 'NA'
# 
#            ")
```

Here, I am going to accomplish the same thing as above, but instead first import each table directly and then combine them using *tidyverse*.

```{r}
demos <- dbGetQuery(con, "SELECT * FROM demos")

responses <- dbGetQuery(con, "SELECT * FROM responses")

socialmedia <- dbGetQuery(con, "SELECT * FROM socialmedia")


tidy_tbl <- responses %>% 
  inner_join(socialmedia, by = c("smu_code" = "code")) %>% 
  inner_join(demos, by = c("ident" = "participant_num")) %>% 
  select(ident, age, facebook, twitter, instagram, youtube, snapchat, other, rec_events, rec_products, rec_friends, rec_policial) #%>% 
  #filter_at(rec_events == "NA")
  

```

Now, *sql_tbl* and *tidy_tbl* are essentially identical. I clean on *tidy_tbl* to prepare for the necessary analysis.

```{r}

clean <-  tidy_tbl %>% 
  select(-ident) %>% 
  mutate_all(funs(
    str_replace(.,
                pattern = "NA|Refused", 
                replacement = NA_character_))) %>% 
  mutate_at(vars(matches("rec")), factor) %>% 
  mutate_at(vars(matches("rec")), as.numeric) %>% 
  mutate(meanPrivacyScore = rowMeans(select(., c(rec_events, rec_products, rec_friends, rec_policial)))) %>% 
  drop_na(meanPrivacyScore) %>% 
  mutate_all(funs(
    str_replace(.,
              pattern = "Not selected",
              replacement = NA_character_))) %>% 
  mutate(smCount = rowSums(!is.na(select(., c(facebook, twitter, instagram, youtube, snapchat, other))))) %>% 
  mutate(age = as.factor(age)) %>% 
  mutate(meanPrivacyScore = as.numeric(meanPrivacyScore)) %>% 
  select(meanPrivacyScore, age, smCount)


# data %>% 
#     rowwise() %>% 
#     mutate(c=mean(c(a,b)))
    
#clean <- import[!(rowSums(is.na(import)) == 10),]

#c(rec_events, rec_products, rec_friends, rec_policial)

```


## Analysis
```{r}
model <- lm(meanPrivacyScore ~ smCount, data = clean)
summary(model)
```


## Visualization
```{r}
ggplot(clean, aes(x = smCount, y = meanPrivacyScore)) + #, col = age)) +
  geom_jitter() + 
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Number of Social Media Platforms Used", y = "Mean Privacy Score")

ggplot(clean, aes(x = smCount, y = meanPrivacyScore, col = age)) +
  geom_jitter() + 
  geom_smooth(method = "lm", se = FALSE) + 
  labs(x = "Number of Social Media Platforms Used", y = "Mean Privacy Score")

ggplot(clean, aes(x = as.factor(smCount), y = meanPrivacyScore)) +
  geom_boxplot() +
  labs(x = "Number of Social Media Platforms Used", y = "Mean Privacy Score")

```

